### 2019-06-26 Sections/index.tex
Cleaning up comments and ???
Quotes, editing
different blind and verification file

@@

\index{Single-photons @\also{Photons}|gobbleone}
\index{Period-finding  @\also{Shor's algorithm}|gobbleone}
\index{Robustness @\also{Network robustness}|gobbleone}
\index{Message digests @\also{Checksum}|gobbleone}
\index{Collisions @\also{Hash collisions}|gobbleone}
\index{Checksum @\also{Hash functions}|gobbleone}
\index{Black box @\also{Oracle}|gobbleone}
\index{Thermal noise @\also{Errors}|gobbleone}
\index{Synthetic aperture @\also{Quantum-enhanced telescopy}|gobbleone}
\index{Ledger @\also{Distributed ledger}|gobbleone}
\index{Integer factorisation @\also{Shor's algorithm}|gobbleone}
\index{Human genome project @\also{Genome}|gobbleone}
\index{Enigma machines @\also{Quantum Enigma machines}|gobbleone}
\index{Efficiency @\also{Loss channel, detector efficiency, computational efficiency}|gobbleone}
\index{Cryptanalysis @\also{Differential cryptanalysis, linear cryptanalysis, frequency analysis}|gobbleone}
\index{Quantum Moore's Law @\also{Moore's Law}|gobbleone}
\index{Toric code @\also{Topological codes, surface codes}|gobbleone}
\index{Surface codes @\also{Topological codes}|gobbleone}
\index{Distributed unitary error averaging @\also{Unitary error averaging}|gobbleone}
\index{Nano-satellites @\also{Micro-satellites}|gobbleone}
\index{Micro-satellites @\also{Nano-satellites}|gobbleone}
\index{Two-channel two-port switches @\also{Optical routers}|gobbleone}
\index{Multiplexers @\also{Optical routers}|gobbleone}
\index{Demultiplexers @\also{Optical routers}|gobbleone}
\index{Linear multiplexers \& demultiplexers @\also{Optical routers}|gobbleone}
\index{Pyramid multiplexers \& demultiplexers @\also{Optical routers}|gobbleone}
\index{Single-channel multi-port switches @\also{Optical routers}|gobbleone}
\index{Multi-channel multi-port switches @\also{Optical routers}|gobbleone}
\index{Quantum error correction (QEC) @\also{3-qubit code, 5-qubit code, 7-qubit code, 9-qubit code, topological codes, unitary error averaging}|gobbleone}
\index{Homomorphic encryption @\also{Encrypted quantum computation}|gobbleone}
\index{Blind quantum computation @\also{Encrypted quantum computation}|gobbleone}
\index{Phase!Key encoding @\also{Encrypted quantum computation}|gobbleone}
\index{Polarisation-key encoding @\also{Encrypted quantum computation}|gobbleone}
\index{Displacement-key encoding @\also{Encrypted quantum computation}|gobbleone}
\index{Non-optical encodings @\also{Matter qubits}|gobbleone}
\index{Time-dependent quantum computational leverage @\also{Quantum computational leverage}|gobbleone}
\index{Distance to horizon @\also{Line-of-sight}|gobbleone}
\index{Line-of-sight @\also{Distance to horizon}|gobbleone}
\index{Micro-cluster states @\also{Star micro-cluster states, plus micro-cluster states, linear micro-cluster states, snowflake micro-cluster states}|gobbleone}
\index{Star micro-cluster states @\also{Micro-cluster states}|gobbleone}
\index{Plus micro-cluster states @\also{Micro-cluster states}|gobbleone}
\index{Linear micro-cluster states @\also{Micro-cluster states}|gobbleone}
\index{Snowflake micro-cluster states @\also{Micro-cluster states}|gobbleone}
\index{Single-qubit quantum computational leverage @\also{Quantum computational leverage}|gobbleone}
\index{Time-dependent quantum computational leverage @\also{Quantum computational leverage}|gobbleone}
\index{Quality of service (QoS) @\also{Quantum error correction, entanglement purification}|gobbleone}
\index{Anonymous surveys @\also{Quantum voting}|gobbleone}
\index{Binary voting @\also{Quantum voting}|gobbleone}

>>>>

\index{Quantum mind \seeonly{Quantum machine learning}|gobbleone}
\index{Quantum state teleportation!Open-destination \seeonly{Open-destination quantum state teleportation}|gobbleone}
\index{Exciton \seeonly{Electron-hole pair}|gobbleone}
\index{Quantum annealing \seeonly{Adiabatic quantum computation}|gobbleone}

@@

\index{Machine learning @\also{Quantum machine learning, classical machine learning}|gobbleone}
\index{Single-photons @\also{Photons}|gobbleone}
\index{Period-finding  @\also{Shor's algorithm}|gobbleone}
\index{Robustness @\also{Network robustness}|gobbleone}
\index{Message digests @\also{Checksum}|gobbleone}
\index{Collisions @\also{Hash collisions}|gobbleone}
\index{Checksum @\also{Hash functions}|gobbleone}
\index{Black box @\also{Oracle}|gobbleone}
\index{Thermal noise @\also{Errors}|gobbleone}
\index{Synthetic aperture @\also{Quantum-enhanced telescopy}|gobbleone}
\index{Ledger @\also{Distributed ledger}|gobbleone}
\index{Integer factorisation @\also{Shor's algorithm}|gobbleone}
\index{Human genome project @\also{Genome}|gobbleone}
\index{Enigma machines @\also{Quantum Enigma machines}|gobbleone}
\index{Efficiency @\also{Loss channel, detector efficiency, computational efficiency}|gobbleone}
\index{Cryptanalysis @\also{Differential cryptanalysis, linear cryptanalysis, frequency analysis}|gobbleone}
\index{Quantum Moore's Law @\also{Moore's Law}|gobbleone}
\index{Toric code @\also{Topological codes, surface codes}|gobbleone}
\index{Surface codes @\also{Topological codes}|gobbleone}
\index{Distributed unitary error averaging @\also{Unitary error averaging}|gobbleone}
\index{Nano-satellites @\also{Micro-satellites}|gobbleone}
\index{Micro-satellites @\also{Nano-satellites}|gobbleone}
\index{Two-channel two-port switches @\also{Optical routers}|gobbleone}
\index{Multiplexers @\also{Optical routers}|gobbleone}
\index{Demultiplexers @\also{Optical routers}|gobbleone}
\index{Linear multiplexers \& demultiplexers @\also{Optical routers}|gobbleone}
\index{Pyramid multiplexers \& demultiplexers @\also{Optical routers}|gobbleone}
\index{Single-channel multi-port switches @\also{Optical routers}|gobbleone}
\index{Multi-channel multi-port switches @\also{Optical routers}|gobbleone}
\index{Quantum error correction (QEC) @\also{3-qubit code, 5-qubit code, 7-qubit code, 9-qubit code, topological codes, unitary error averaging}|gobbleone}
\index{Homomorphic encryption @\also{Encrypted quantum computation}|gobbleone}
\index{Blind quantum computation @\also{Encrypted quantum computation}|gobbleone}
\index{Phase!Key encoding @\also{Encrypted quantum computation}|gobbleone}
\index{Polarisation-key encoding @\also{Encrypted quantum computation}|gobbleone}
\index{Displacement-key encoding @\also{Encrypted quantum computation}|gobbleone}
\index{Non-optical encodings @\also{Matter qubits}|gobbleone}
\index{Time-dependent quantum computational leverage @\also{Quantum computational leverage}|gobbleone}
\index{Distance to horizon @\also{Line-of-sight}|gobbleone}
\index{Line-of-sight @\also{Distance to horizon}|gobbleone}
\index{Micro-cluster states @\also{Star micro-cluster states, plus micro-cluster states, linear micro-cluster states, snowflake micro-cluster states}|gobbleone}
\index{Star micro-cluster states @\also{Micro-cluster states}|gobbleone}
\index{Plus micro-cluster states @\also{Micro-cluster states}|gobbleone}
\index{Linear micro-cluster states @\also{Micro-cluster states}|gobbleone}
\index{Snowflake micro-cluster states @\also{Micro-cluster states}|gobbleone}
\index{Single-qubit quantum computational leverage @\also{Quantum computational leverage}|gobbleone}
\index{Time-dependent quantum computational leverage @\also{Quantum computational leverage}|gobbleone}
\index{Quality of service (QoS) @\also{Quantum error correction, entanglement purification}|gobbleone}
\index{Anonymous surveys @\also{Quantum voting}|gobbleone}
\index{Binary voting @\also{Quantum voting}|gobbleone}

### 2019-06-26 Sections/intro_to_QM.tex
different blind and verification file

In quantum mechanics the discrete-time evolution of an $N$-dimensional state is given by arbitrary \mbox{$N\times N$}-dimensional unitary transformations\index{Unitary!Operators}, $\mathrm{U}(N)$, which satisfy,
\begin{align}
\hat{U}^\dag\hat{U}=\hat\openone.	
\end{align}

>>>>

In quantum mechanics the discrete-time evolution of an $N$-dimensional state is given by arbitrary \mbox{$N\times N$}-dimensional unitary transformations\index{Unitary!Operators}, $\mathrm{U}(N)$, satisfying,
\begin{align}
\hat{U}^\dag\hat{U}=\hat\openone.	
\end{align}

### 2019-06-26 Sections/mathematical_representation_of_quantum_networks.tex
different blind and verification file

We consider a classical network to be a weighted, directed graph,
\begin{align}\index{Network!Graphs}\index{Graphs}
	G=(V,E),
\end{align}
where vertices represent \textit{nodes} (\mbox{$v\in V$}) in the network, and the weighted edges represent communication \textit{links} (\mbox{$e\in E$}) between neighbouring nodes \cite{???}.

@@

On a shared network with many users utilising the network simultaneously, it may be the case that the preferred goal for the network is to maximise \textit{flow} \cite{???} -- the total amount of information that can be transmitted per unit time, i.e the net utilisation of the network's resources, summed over all users. In this case we can build on the existing theory of \textit{flow networks} \cite{???}, which characterise the load of links within the network.

@@

If one were to become even more sophisticated, one might even envisage treating network resource allocation in a game theoretic context \cite{???}, which we won't even begin to delve into here.

>>>>

We consider a classical network to be a weighted, directed graph,
\begin{align}\index{Network!Graphs}\index{Graphs}
	G=(V,E),
\end{align}
where vertices represent \textit{nodes} (\mbox{$v\in V$}) in the network, and the weighted edges represent communication \textit{links} (\mbox{$e\in E$}) between neighbouring nodes.

@@

On a shared network with many users utilising the network simultaneously, it may be the case that the preferred goal for the network is to maximise \textit{flow} -- the total amount of information that can be transmitted per unit time, i.e the net utilisation of the network's resources, summed over all users. In this case we can build on the existing theory of \textit{flow networks} \cite{???}, which characterise the load of links within the network.

@@

If one were to become even more sophisticated, one might even envisage treating network resource allocation in a game theoretic context, which we won't even begin to delve into here.

### 2019-06-26 Sections/optical_stability_in_quantum_networks.tex
different blind and verification file

Before describing optical interference in detail, we must first formalise a definition for the optical wave-packets we will be dealing with. We will assume wave-packets with Gaussian temporal envelope of width $\sigma$ (the coherence length\index{Coherence length}), frequency-shifted by some carrier frequency $\omega_0$ (the wavelength\index{Wavelength}).

@@

\startnormtable
\begin{table}[!htbp]
	\begin{tabular}{|c|c|}
		\hline
  		\rowcolor{Dandelion} Protocol & Interference type \\
  		\hline
  		\hline
  		\rowcolor{LimeGreen} Cluster state measurement & None \\
   		\rowcolor{LimeGreen} Quantum anonymous broadcasting & None \\
  		\rowcolor{LimeGreen} QKD (BB84, E91) & None \\
  		\rowcolor{LimeGreen} Quantum memory & None \\
  		\rowcolor{LimeGreen} Quantum process tomography & None \\
  		\rowcolor{LimeGreen} Quantum state tomography & None \\
  		\rowcolor{LimeGreen} Random number generation & None \\
  		\rowcolor{LimeGreen} Separable measurements & None \\
  		\rowcolor{LimeGreen} Separable state preparation & None \\
  		\rowcolor{LimeGreen} Optical interfacing & None \\
  		\hline
  		\rowcolor{Apricot} Cluster state preparation (fusion gates) & HOM \\
  		\rowcolor{Apricot} Entanglement purification & HOM \\
  		\rowcolor{Apricot} Entanglement swapping & HOM \\ 
  		\rowcolor{Apricot} Matter qubit entangling operations & HOM \\
  		\rowcolor{Apricot} Partial Bell state measurements & HOM \\
   		\rowcolor{Apricot} Quantum gate teleportation & HOM \\
  		\rowcolor{Apricot} Quantum state teleportation & HOM \\
  		\rowcolor{Apricot} Superdense coding & HOM \\
  		\hline
  		\rowcolor{Lavender} \textsc{BosonSampling} & MZ \\
  		\rowcolor{Lavender} General linear optics networks & MZ \\
  		\rowcolor{Lavender} Universal LOQC (KLM) & MZ \\
  		\rowcolor{Lavender} Quantum metrology & MZ \\
  		\rowcolor{Lavender} Quantum walks & MZ \\
    	\hline
	\end{tabular}
	\captionspacetab \caption{Summary of the major quantum network protocols presented in Part.~\ref{part:protocols}, and their required type of interference.}\index{Interferometric requirements}\label{table:summary_inter}
\end{table}

>>>>

Before describing optical interference in detail, we must first formalise a definition for the optical wave-packets we will be dealing with. We will assume wave-packets with Gaussian temporal envelope of width $\sigma$ (the coherence length\index{Coherence!Length}), frequency-shifted by some carrier frequency $\omega_0$ (the wavelength\index{Wavelength}).

@@

\startnormtable
\begin{table}[!htbp]
	\begin{tabular}{|c|c|}
		\hline
  		\rowcolor{Dandelion} Protocol & Interference type \\
  		\hline
  		\hline
  		\rowcolor{LimeGreen} Cluster state measurement & None \\
   		\rowcolor{LimeGreen} Quantum anonymous broadcasting & None \\
  		\rowcolor{LimeGreen} QKD (BB84, E91) & None \\
  		\rowcolor{LimeGreen} Quantum memory & None \\
  		\rowcolor{LimeGreen} Quantum process tomography & None \\
  		\rowcolor{LimeGreen} Quantum state tomography & None \\
  		\rowcolor{LimeGreen} Random number generation & None \\
  		\rowcolor{LimeGreen} Separable measurements & None \\
  		\rowcolor{LimeGreen} Separable state preparation & None \\
  		\rowcolor{LimeGreen} Optical interfacing & None \\
  		\hline
  		\rowcolor{Apricot} Cluster state preparation (fusion gates) & HOM \\
  		\rowcolor{Apricot} Entanglement purification & HOM \\
  		\rowcolor{Apricot} Entanglement swapping & HOM \\ 
  		\rowcolor{Apricot} Matter qubit entangling operations & HOM \\
  		\rowcolor{Apricot} Partial Bell state measurements & HOM \\
   		\rowcolor{Apricot} Quantum gate teleportation & HOM \\
  		\rowcolor{Apricot} Quantum state teleportation & HOM \\
  		\rowcolor{Apricot} Superdense coding & HOM \\
  		\hline
  		\rowcolor{Lavender} \textsc{BosonSampling} & MZ \\
  		\rowcolor{Lavender} General linear optics networks & MZ \\
  		\rowcolor{Lavender} Universal LOQC (KLM) & MZ \\
  		\rowcolor{Lavender} Quantum metrology & MZ \\
  		\rowcolor{Lavender} Quantum walks & MZ \\
    	\hline
	\end{tabular}
	\captionspacetab \caption{Summary of the major quantum network protocols presented in Part.~\ref{part:protocols}, and their required type of interference.}\index{Interferometric!Requirements}\label{table:summary_inter}
\end{table}

### 2019-06-26 Sections/publication_mode.tex
different blind and verification file

% Specify configuration: (0 = off, 1 = on)
% 	sketchesmode 		= Sketches?
% 	seriousmode 		= Serious?
% 	maincontribstyle 	= Main/contributed or unified authorship list?
% 	QIPlink 			= Title page link to QIP project website?
% 	parainTOC 			= Paragraphs included in ToC?
% 	includelicense		= Creative Commons license page?

% Draft without figures
\if 0\pubmode
	\def\sketchesmode{0} 		% Sketches?
	\def\seriousmode{0} 			% Serious?
	\def\maincontribstyle{0} 	% Main/contributed or unified authorship list?
	\def\QIPlink{1} 			% Title page link to QIP project website?
	\def\parainTOC{0} 			% Paragraphs included in ToC?
	\def\includelicense{0}		% Creative Commons license page?

	\documentclass[draft, twocolumn, aps, rmp, amsmath, amssymb, nofootinbib, superscriptaddress, longbibliography, floatfix, table-of-contents, eqsecnum]{revtex4-1}
	\let\stdsection\section
	\renewcommand\section{\newpage\stdsection}
\fi

% Dowling's eyes only
\if 1\pubmode
	\def\sketchesmode{0} 		% Sketches?
	\def\seriousmode{1}	 		% Serious?
	\def\maincontribstyle{0} 	% Main/contributed or unified authorship list?
	\def\QIPlink{0} 			% Title page link to QIP project website?
	\def\parainTOC{0} 			% Paragraphs included in ToC?
	\def\includelicense{0}		% Creative Commons license page?

	\documentclass[preprint, aps, rmp, singlecolumn, amsmath, amssymb, nofootinbib, superscriptaddress, longbibliography, floatfix, table-of-contents, eqsecnum]{revtex4-1}
\fi

% Serious draft
\if 2\pubmode
	\def\sketchesmode{0} 		% Sketches?
	\def\seriousmode{1} 			% Serious?
	\def\maincontribstyle{0} 	% Main/contributed or unified authorship list?
	\def\QIPlink{1} 			% Title page link to QIP project website?
	\def\parainTOC{0} 			% Paragraphs included in ToC?
	\def\includelicense{1}		% Creative Commons license page?

	\documentclass[twocolumn, aps, rmp, amsmath, amssymb, nofootinbib, superscriptaddress, longbibliography, floatfix, table-of-contents, eqsecnum]{revtex4-1}
\fi

% Arxiv
\if 3\pubmode
	\def\sketchesmode{1} 		% Sketches?
	\def\seriousmode{0} 			% Serious?
	\def\maincontribstyle{0} 	% Main/contributed or unified authorship list?
	\def\QIPlink{1} 			% Title page link to QIP project website?
	\def\parainTOC{0} 			% Paragraphs included in ToC?
	\def\includelicense{1}		% Creative Commons license page?

	\documentclass[twocolumn, aps, rmp, amsmath, amssymb, nofootinbib, superscriptaddress, longbibliography, floatfix, table-of-contents, eqsecnum]{revtex4-1}
\fi

% Publisher
\if 4\pubmode 
	\def\sketchesmode{1} 		% Sketches?
	\def\seriousmode{0} 			% Serious?
	\def\maincontribstyle{1} 	% Main/contributed or unified authorship list?
	\def\QIPlink{0} 			% Title page link to QIP project website?
	\def\parainTOC{0} 			% Paragraphs included in ToC?
	\def\includelicense{0}		% Creative Commons license page?

	\documentclass[singlecolumn, aps, rmp, amsmath, amssymb, nofootinbib, superscriptaddress, longbibliography, floatfix, table-of-contents, eqsecnum]{revtex4-1}
	\let\stdpart\part
	\renewcommand\part{\newpage\stdpart}
\fi

>>>>

% Specify configuration: (0 = off, 1 = on)
% 	sketchesmode 		= Sketches?
% 	seriousmode 		= Serious?
% 	maincontribstyle 	= Main/contributed or unified authorship list?
% 	QIPlink 			= Title page link to QIP project website?
% 	parainTOC 			= Paragraphs included in ToC?
% 	includelicense		= Creative Commons license page?
%	doublecol			= Two-column?

% Draft without figures
\if 0\pubmode
	\def\sketchesmode{0} 		% Sketches?
	\def\seriousmode{0} 			% Serious?
	\def\maincontribstyle{0} 	% Main/contributed or unified authorship list?
	\def\QIPlink{1} 			% Title page link to QIP project website?
	\def\parainTOC{0} 			% Paragraphs included in ToC?
	\def\includelicense{0}		% Creative Commons license page?
	\def\doublecol{1}

	\documentclass[draft, twocolumn, aps, rmp, amsmath, amssymb, nofootinbib, superscriptaddress, longbibliography, floatfix, table-of-contents, eqsecnum]{revtex4-2}
	\let\stdsection\section
	\renewcommand\section{\newpage\stdsection}
\fi

% Dowling's eyes only
\if 1\pubmode
	\def\sketchesmode{0} 		% Sketches?
	\def\seriousmode{1}	 		% Serious?
	\def\maincontribstyle{0} 	% Main/contributed or unified authorship list?
	\def\QIPlink{0} 			% Title page link to QIP project website?
	\def\parainTOC{0} 			% Paragraphs included in ToC?
	\def\includelicense{0}		% Creative Commons license page?
	\def\doublecol{0}

	\documentclass[preprint, aps, rmp, singlecolumn, amsmath, amssymb, nofootinbib, superscriptaddress, longbibliography, floatfix, table-of-contents, eqsecnum]{revtex4-2}
\fi

% Serious draft
\if 2\pubmode
	\def\sketchesmode{0} 		% Sketches?
	\def\seriousmode{1} 			% Serious?
	\def\maincontribstyle{0} 	% Main/contributed or unified authorship list?
	\def\QIPlink{1} 			% Title page link to QIP project website?
	\def\parainTOC{0} 			% Paragraphs included in ToC?
	\def\includelicense{1}		% Creative Commons license page?
	\def\doublecol{1}

	\documentclass[twocolumn, aps, rmp, amsmath, amssymb, nofootinbib, superscriptaddress, longbibliography, floatfix, table-of-contents, eqsecnum]{revtex4-2}
\fi

% Arxiv
\if 3\pubmode
	\def\sketchesmode{1} 		% Sketches?
	\def\seriousmode{0} 			% Serious?
	\def\maincontribstyle{0} 	% Main/contributed or unified authorship list?
	\def\QIPlink{1} 			% Title page link to QIP project website?
	\def\parainTOC{0} 			% Paragraphs included in ToC?
	\def\includelicense{1}		% Creative Commons license page?
	\def\doublecol{1}

	\documentclass[twocolumn, aps, rmp, amsmath, amssymb, nofootinbib, superscriptaddress, longbibliography, floatfix, table-of-contents, eqsecnum]{revtex4-2}
\fi

% Publisher
\if 4\pubmode 
	\def\sketchesmode{1} 		% Sketches?
	\def\seriousmode{0} 			% Serious?
	\def\maincontribstyle{1} 	% Main/contributed or unified authorship list?
	\def\QIPlink{0} 			% Title page link to QIP project website?
	\def\parainTOC{0} 			% Paragraphs included in ToC?
	\def\includelicense{0}		% Creative Commons license page?
	\def\doublecol{0}

	\documentclass[singlecolumn, aps, rmp, amsmath, amssymb, nofootinbib, superscriptaddress, longbibliography, floatfix, table-of-contents, eqsecnum]{revtex4-2}
	\let\stdpart\part
	\renewcommand\part{\newpage\stdpart}
\fi

### 2019-06-26 Sections/quantum_crypto_assets.tex
different blind and verification file

Suppose Alice wishes to store quantum data offsite, for example in a repository for safekeeping, or within remote or decentralised data structures (such as a Blockchain\index{Blockchain}). Since her data is not held locally, there is the concern that an unauthorised third party might simply steal it. How can she ensure its integrity, without maintaining any quantum data (assuming she can locally maintain classical data)?

@@

From her perspective (or anyone she chooses to share the 2 classical bits with), she is always able to perfectly recover the hidden qubit, simply by applying the same Pauli operators a second time to invert them. However, from the perspective of a third party without access to the 2 classical bits, they observe a perfect depolarising channel\index{Depolarising channel},
\begin{align}
	\mathcal{E}^\text{depolarising}_{0}(\hat\rho) = \frac{\hat\openone}{4},
\end{align}
yielding the completely mixed state, independent of the input state, from which no state information can be inferred. Thus, this approach confers \textit{perfect} information-theoretic security\index{Information-theoretic security}.

@@

It's essential that such exchanges be performed with integrity, such that in a potentially anonymous transaction one party cannot run off with everything. The obvious solution here is to employ a trusted third party to mediate the transaction, as is done in many real-world high-value exchanges. But this in undesirable for several reasons:
\begin{itemize}
\item Trust\index{Trust}: Both parties must have complete confidence in the integrity of the mediating third party. This necessarily introduces risk, which manifests itself as an indirect transaction cost.
\item Monetary cost: A third party is most likely to charge for the service they provide. Even if this margin is slim, in high-volume markets this becomes a consideration.
\item Latency\index{Latency}: Mediation introduces an additional layer of communication, with associated latency. Even in today's high-frequency markets, minute latency improvements yield major competitive advantage.
\item Resource overheads: Mediation imposes greater resource requirements, most notably communication or computational ones.
\item Regulatory\index{Regulations}: `Credible' mediators typically comply with regulatory and taxation agencies. Traders of an anarcho-capitalistic\index{Anarcho-capitalism} mindset would rather avoid such nonsense altogether, and establish a truly globalised free-market. \latinquote{Lux libertas. Lux tua nos ducat.}
\end{itemize}
This motivates the question, can we securely implement \textit{direct} exchanges, in the absence of any trusted mediating authority or regulatory oversight?

>>>>

Suppose Alice wishes to store quantum data offsite, for example in a repository for safekeeping, or within remote or decentralised data structures (such as a Blockchain\index{Blockchain}). Since her data is not held locally, there is the concern that an unauthorised third-party might simply steal it. How can she ensure its integrity, without maintaining any quantum data (assuming she can locally maintain classical data)?

@@

From her perspective (or anyone she chooses to share the 2 classical bits with), she is always able to perfectly recover the hidden qubit, simply by applying the same Pauli operators a second time to invert them. However, from the perspective of a third-party without access to the 2 classical bits, they observe a perfect depolarising channel\index{Depolarising channel},
\begin{align}
	\mathcal{E}^\text{depolarising}_{0}(\hat\rho) = \frac{\hat\openone}{4},
\end{align}
yielding the completely mixed state, independent of the input state, from which no state information can be inferred. Thus, this approach confers \textit{perfect} information-theoretic security\index{Information-theoretic security}.

@@

It's essential that such exchanges be performed with integrity, such that in a potentially anonymous transaction one party cannot run off with everything. The obvious solution here is to employ a trusted third-party to mediate the transaction, as is done in many real-world high-value exchanges. But this in undesirable for several reasons:
\begin{itemize}
\item Trust\index{Trust}: Both parties must have complete confidence in the integrity of the mediating third-party. This necessarily introduces risk, which manifests itself as an indirect transaction cost.
\item Monetary cost: A third-party is most likely to charge for the service they provide. Even if this margin is slim, in high-volume markets this becomes a consideration.
\item Latency\index{Latency}: Mediation introduces an additional layer of communication, with associated latency. Even in today's high-frequency markets, minute latency improvements yield major competitive advantage.
\item Resource overheads: Mediation imposes greater resource requirements, most notably communication or computational ones.
\item Regulatory\index{Regulations}: `Credible' mediators typically comply with regulatory and taxation agencies. Traders of an anarcho-capitalistic\index{Anarcho-capitalism} mindset would rather avoid such nonsense altogether, and establish a truly globalised free-market. \latinquote{Lux libertas. Lux tua nos ducat.}
\end{itemize}
This motivates the question, can we securely implement \textit{direct} exchanges, in the absence of any trusted mediating authority or regulatory oversight?

### 2019-06-26 Sections/roadmap.tex
Tech-web
appendix
tiny
+quotes, formatting
different blind and verification file

\part{Roadmap -- The way forward}\index{Roadmap}

>>>>

\part{Roadmap -- The way forward}\index{Roadmap}\label{part:roadmap}

\famousquote{You got to go down a lot of wrong roads to find the right one.}{Bob Parsons}
\newline

\famousquote{The further a society drifts from the truth, the more it will hate those that speak it.}{George Orwell}

\section{The tech-web for the quantum future}

### 2019-06-26 Sections/state_of_the_art.tex
ZKP++
different blind and verification file

\sectionby{He-Liang Huang \& Zu-en Su}

@@

		%Entanglement swapping can also be directly used for QKD. Alice and Bob each have an entangled photon source, and one photon of each Bell pair is sent to a third-party measurement node, Eve. Similar to measurement-device-independent (MDI) QKD, the security of the generated private key does not depend on Eve's faithful execution of the operation. That is, Eve can be an untrusted third party. This MDI property also reflects the physical beauty of quantum teleportation. Bell state measurements do not reveal any information about the quantum state, but can be used to restore the transmitted quantum state. On the other hand, quantum entanglement occurs between the remaining photons in the Bell pair of Alice and Bob.

@@

\begin{table*}[!htbp]
	\begin{tabular}{|p{0.755\linewidth}|p{0.22\linewidth}|}
		\hline
	\textbf{Summary} & \textbf{References \& years} \\	\hline \hline
		\textit{Single photon avalanche diodes (SPAD) --}
		SPADs are the most compact and common single-photon detectors in the world. Commercially, silicon SPADs are available with detection efficiency around 60\% at 780nm, maximum count rates of 25MHz and dark count rates as low as 25Hz. Several remarks are:

>>>>

\sectionby{He-Liang Huang \& Zu-en Su}\index{He-Liang Huang}\index{Zu-en Su}

@@

		%Entanglement swapping can also be directly used for QKD. Alice and Bob each have an entangled photon source, and one photon of each Bell pair is sent to a third-party measurement node, Eve. Similar to measurement-device-independent (MDI) QKD, the security of the generated private key does not depend on Eve's faithful execution of the operation. That is, Eve can be an untrusted third-party. This MDI property also reflects the physical beauty of quantum teleportation. Bell state measurements do not reveal any information about the quantum state, but can be used to restore the transmitted quantum state. On the other hand, quantum entanglement occurs between the remaining photons in the Bell pair of Alice and Bob.

@@

\begin{table*}[!htbp]
	\begin{tabular}{|p{0.755\linewidth}|p{0.22\linewidth}|}
		\hline
	\textbf{Summary} & \textbf{References \& years} \\	\hline \hline
		\textit{Single photon avalanche diodes (SPAD) --}
		SPADs are the most compact and common single-photon detectors in the world. Commercially, silicon SPADs are available with detection efficiency around 60\% at 780nm, maximum count rates of 25MHz and dark-count rates as low as 25Hz. Several remarks are:

### 2019-06-26 Sections/wine_pairings.tex
different blind and verification file

\dropcap{L}{ike} any good meal, any good book chapter is best paired with a suitably-chosen wine that compliments its unique notes and characteristics. Here we suggest several contemporary, budget-friendly, Australian wines, hand-selected by the authors, that perfectly match the subtle undertones of each part in the book.

>>>>

\dropcap{L}{ike} any good meal, a good book chapter is best paired with a suitably-chosen wine that compliments its unique notes and characteristics. Ancient tradition tells us that this enhances the quality of the reader's interpretation, making a given text be perceived as far more remarkable and ingenious than it ordinarily would be. Here we suggest several contemporary, budget-friendly, Australian wines, hand-selected by the authors, that perfectly match the subtle undertones of each part in the book.
